hbm_paper_results

### 2024-06-19 paper_main_results.Rmd
presentation figs

>>>>

# Other Figs
Plotting normal curves for pres

```{r}
data <- data.frame(A = rnorm(1000000, mean = 7, sd = .5),
                   B = rnorm(1000000, mean = 10, sd = 2),
                   C = rnorm(1000000, mean = 13, sd = 3.5),
                   datatype=rep("raw", n=1000000))

ggplot(data, aes(x = A)) +
  geom_density(fill = "gray", alpha = 0.5, size=4) +
  geom_vline(xintercept = mean(data$A), size=1) +
  labs(x = "Value",
       y = "Density") +
  xlim(4, 20) +
  theme_void()

ggplot(data, aes(x = B)) +
  geom_density(fill = "gray", alpha = 0.5, size=4) +
  geom_vline(xintercept = mean(data$B), size=1) +
  labs(x = "Value",
       y = "Density") +
  xlim(4, 20) +
  theme_void()

ggplot(data, aes(x = C)) +
  geom_density(fill = "gray", alpha = 0.5, size=4) +
  geom_vline(xintercept = mean(data$C), size=1) +
  labs(x = "Value",
       y = "Density") +
  xlim(4, 20) +
  theme_void()
```

```{r}
combatgam_data <- data.frame(A = rnorm(1000000, mean = 9.5, sd = 2),
                   B = rnorm(1000000, mean = 10, sd = 2),
                   C = rnorm(1000000, mean = 11, sd = 2),
                   datatype=rep("cf.gam", n=1000000))

combatgam_data <- full_join(combatgam_data, data) %>%
  mutate(datatype=factor(datatype, levels=c("raw", "cf.gam"), ordered=T))
```

```{r}
combatgam_data %>%
ggplot(aes(fill=datatype, color=datatype)) +
  geom_density(aes(x=A), alpha = 0.5, size=4) +
  geom_vline(xintercept = mean(combatgam_data[combatgam_data$datatype=="raw",]$A), size=1, color="black") +
  geom_vline(xintercept = mean(combatgam_data[combatgam_data$datatype=="cf.gam",]$A), size=1, color="#3D75C2") +
scale_color_manual(values = c(cf.gam = "#3D75C2", raw= "black", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF")) +
  scale_fill_manual(values = c(cf.gam = "#3D75C2",raw= "gray", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF")) +
  labs(x = "Value",
       y = "Density") +
  xlim(4, 20) +
  theme_void() +
  theme(legend.position="none")

combatgam_data %>%
ggplot(aes(fill=datatype, color=datatype)) +
  geom_density(aes(x=B), alpha = 0.5, size=4) +
  geom_vline(xintercept = mean(combatgam_data[combatgam_data$datatype=="raw",]$B), size=1, color="black") +
  geom_vline(xintercept = mean(combatgam_data[combatgam_data$datatype=="cf.gam",]$B), size=1, color="#3D75C2") +
scale_color_manual(values = c(cf.gam = "#3D75C2", raw= "black", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF")) +
  scale_fill_manual(values = c(cf.gam = "#3D75C2",raw= "gray", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF")) +
  labs(x = "Value",
       y = "Density") +
  xlim(4, 20) +
  theme_void() +
  theme(legend.position="none")

combatgam_data %>%
ggplot(aes(fill=datatype, color=datatype)) +
  geom_density(aes(x=C), alpha = 0.5, size=4) +
  geom_vline(xintercept = mean(combatgam_data[combatgam_data$datatype=="raw",]$C), size=1, color="black") +
  geom_vline(xintercept = mean(combatgam_data[combatgam_data$datatype=="cf.gam",]$C), size=1, color="#3D75C2") +
scale_color_manual(values = c(cf.gam = "#3D75C2", raw= "black", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF")) +
  scale_fill_manual(values = c(cf.gam = "#3D75C2",raw= "gray", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF")) +
  labs(x = "Value",
       y = "Density") +
  xlim(4, 20) +
  theme_void() +
  theme(legend.position="none")
```

```{r}
combatgamlss_data <- data.frame(A = rnorm(1000000, mean = 9.5, sd = 1),
                   B = rnorm(1000000, mean = 10, sd = 2),
                   C = rnorm(1000000, mean = 11, sd = 3),
                   datatype=rep("cf.gamlss", n=1000000))

combatgamlss_data <- full_join(combatgamlss_data, data) %>%
  mutate(datatype=factor(datatype, levels=c("raw", "cf.gamlss"), ordered=T))
```

```{r}
combatgamlss_data %>%
ggplot(aes(fill=datatype, color=datatype)) +
  geom_density(aes(x=A), alpha = 0.5, size=4) +
  geom_vline(xintercept = mean(combatgamlss_data[combatgamlss_data$datatype=="raw",]$A), size=1, color="black") +
  geom_vline(xintercept = mean(combatgamlss_data[combatgamlss_data$datatype=="cf.gamlss",]$A), size=1, color="#CFB023FF") +
scale_color_manual(values = c(cf.gam = "#3D75C2", raw= "black", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF")) +
  scale_fill_manual(values = c(cf.gam = "#3D75C2",raw= "gray", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF")) +
  labs(x = "Value",
       y = "Density") +
  xlim(4, 20) +
  theme_void() +
  theme(legend.position="none")

combatgamlss_data %>%
ggplot(aes(fill=datatype, color=datatype)) +
  geom_density(aes(x=B), alpha = 0.5, size=4) +
  geom_vline(xintercept = mean(combatgamlss_data[combatgamlss_data$datatype=="raw",]$B), size=1, color="black") +
  geom_vline(xintercept = mean(combatgamlss_data[combatgamlss_data$datatype=="cf.gamlss",]$B), size=1, color="#CFB023FF") +
scale_color_manual(values = c(cf.gam = "#3D75C2", raw= "black", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF")) +
  scale_fill_manual(values = c(cf.gam = "#3D75C2",raw= "gray", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF")) +
  labs(x = "Value",
       y = "Density") +
  xlim(4, 20) +
  theme_void() +
  theme(legend.position="none")

combatgamlss_data %>%
ggplot(aes(fill=datatype, color=datatype)) +
  geom_density(aes(x=C), alpha = 0.5, size=4) +
  geom_vline(xintercept = mean(combatgamlss_data[combatgamlss_data$datatype=="raw",]$C), size=1, color="black") +
  geom_vline(xintercept = mean(combatgamlss_data[combatgamlss_data$datatype=="cf.gamlss",]$C), size=1, color="#CFB023FF") +
scale_color_manual(values = c(cf.gam = "#3D75C2", raw= "black", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF")) +
  scale_fill_manual(values = c(cf.gam = "#3D75C2",raw= "gray", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF")) +
  labs(x = "Value",
       y = "Density") +
  xlim(4, 20) +
  theme_void() +
  theme(legend.position="none")
```

```{r}
data2 <- data.frame(d = rnorm(1000000, mean = 0, sd = 1)) %>%
  mutate(sd_cat = if_else(d < (0-1.7) | d > (0+1.7),"ext", "not_ext"))

data2 %>%
ggplot(aes(size=1.4), color="black")+
  geom_density(aes(x=d), alpha = 0.5, fill="gray") +
  geom_vline(xintercept = (0-1.65), size=1, color="#CFB023FF") +
  geom_vline(xintercept = (0+1.65), size=1, color="#CFB023FF")+
  theme_void()

data2 %>%
ggplot(aes(size=1.4), color="black")+
  geom_density(aes(x=d), alpha = 0.5, fill="gray") +
  geom_vline(xintercept = (0-1.65), size=1, color="#3D75C2") +
  geom_vline(xintercept = (0+1.65), size=1, color="#3D75C2")+
  theme_void()

data2 %>%
ggplot(aes(size=1.4), color="black")+
  geom_density(aes(x=d), alpha = 0.5) +
  theme_void()
```
